3-advanced

### 2022-06-17 3-advanced.Rmd

```{r illu-interactive, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "An illustration of the data model under interactive graphics with cubble. The line plot and the map is made separately with the long and nested cubble. When a station is selected on the map (left), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (middle) and update the line plot (right)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.003.png"))
```

>>>>

```{r illu-interactive, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "Linking between multiple plots. The line plots and the map are constructed from shared crosstalk objects (long and nested cubbles). When a station is selected on the map (a), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (b) and update the line plot (c)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.004.png"))
```
